---
title: "almond_AC"
author: "AnnaClaire Marley"
date: "4/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include = FALSE}
# load packages
library(tidyverse)
library(pse)

# source function
source('~/Documents/github/almond_sensitivity/almond_anomaly.R')
```

## Sensitivity Analysis on Almond Yield Function

* **Perform a sensitivity analysis of how mean anomaly varies all of the parameters used in the almond yield model**
* **Assume parameters are normally distributed with standard deviation of 20% mean value**

#### **Latin Hypercube Method**

```{r}

# All parameters of almond yield model
factors = c("a", "b", "c", "d", "e")

# Decide How many parameter sets to run
nsets = 100

# choose distributions for parameters - 
q = c("qnorm", "qnorm", "qnorm", "qnorm", "qnorm")
q.arg = list(list(mean = -0.015, sd = 0.20), 
             list(mean = -0.0046, sd = 0.20), 
             list(mean = -0.07, sd = 0.20),
             list(mean = 0.0043, sd = 0.20), 
             list(mean = 99999, sd = 0.20))

# generate samples from LHS
sens_almond = LHS(NULL, factors, nsets, q, q.arg)

# set of values generaated for each parameter
sens_pars = get.data(sens_almond)
head(sens_pars)

# now run the model for each set of parameter samples
# first create a data structure to store results
sens_results = matrix(nrow=nsets, ncol=1)

# read in the input data
clim <- read.table("clim.txt")

# run the almond yield model for each parameter set
tmp = mapply(FUN=almond_anomaly, 
             a = sens_pars$a, 
             b = sens_pars$b, 
             c = sens_pars$c, 
             d = sens_pars$d,
             e = sens_pars$e,
             MoreArgs=list(clim_data = clim,
                           mean_only = TRUE))
head(tmp)

# turn into matrix using unlist 
sens_results_LH = matrix((unlist(tmp)), ncol=1, byrow=TRUE)
colnames(sens_results_LH) = c("mean_yield")


```

**Rank the parameters in term of their sensitivity**

```{r}

# send results back
sens_almond = pse::tell(sens_almond, t(sens_results_LH), 
                        res.names=c("mean_yield"))
# plot sensitivity
pse::plotscatter(sens_almond, col="blue", cex=5)

# Plot the partial rank correlation coefficient
pse::plotprcc(sens_almond)
sens_almond$prcc

```

Sensitivity ranking

* 1) d (precip coefficient) 
* 2) e (model intercept) 
* 3) a (temp coefficient)
* 4) b (temp coefficient) 
* 5) c (precip coefficient) 

**Graph uncertainty in mean yield anomaly across all parameter uncertainty (boxplot and cummulative distribution of the output).**

```{r}
# make it a dataframe
sens_results_LH = as.data.frame(sens_results_LH)

# plot it
  ggplot(data = sens_results_LH, aes(x = " ", y = mean_yield)) +
    geom_boxplot(fill = "brown") +
    labs( 
     title = "Latin Hypercube Uncertainty",
      x = "Almond",
      y = "Yield (as anomoly)"
      ) +
    theme_classic()

```


#### **Sobel method**

```{r}

```



Repeat using twice as many parameter sets as you did in your first sensitivity analysis - and look at how this changes the sensitivity results
